### 2016-10-05 robust-software.tex
Installing dependencies

\item
Recommend that people \emph{always} install dependencies, even on their own machine,
using their equivalent of \texttt{requirements.txt}
so that they're sure it works.

@@

This file can be read by a package manager, which can check that the
required software is available, and install it if it is not. Similar
mechanisms exist for Perl, R, and other languages.

>>>>

@@

This file can be read by a package manager, which can check that the
required software is available, and install it if it is not. Similar
mechanisms exist for Perl, R, and other languages.  Whatever is used,
we recommend that developers should \emph{always} install dependencies
using this mechanism, especially on their personal machines, so that
they're sure it works.
